Generating the Blueprints of the Java Ecosystem

### 2015-02-26 msr.tex
added research opportunities

@@

The Java platform exists for more than a decade and provides a development environment for several application areas, such as the web, grid computing, and traditional client-server applications.
% dimitro@bkarak: references here.
The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}.

% dimitro@bkarak: I cannot see the connection of the above paragraph with the following.

By using the dataset, one small problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects. In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.

>>>>

\section{Research Opportunities}
\label{sec:research-opportunities}

@@
